Timeliness of security updates for Android

### 2014-08-11 security_scoring.tex
Add note on gaming DA
Touch up security scoring section

This score is computed from several components:
\begin{description}
  \item[$f$] The proportion of the time where devices were free from known critical vulnerabilities. This is equivalent to Acer and Jackson's proposal~\cite{Acer2010} to measure the security based on the proportion of users with at least one unpatched critical vulnerability and to the Vulnerability Free Days (VFD) score~\cite{Wright2014}.
  Unlike VFD this is the proportion of running devices which were free from critical vulnerabilities, rather than days which the manufacturer was free from outstanding critical vulnerabilities as that does not take account of the update process.
  \item[$u$] The proportion of devices run the latest version of Android shipped to any device produced by that manufacturer. This is a measure of internal updatedness, a low score would mean many devices are being left behind.
  This assumes that newer versions are better with stronger security, historically steps have been taken to improve Android security in newer versions so this assumption should generally hold, but sometimes new updates introduce new vulnerabilities.
  \item[$m$] The mean number of outstanding vulnerabilities affecting devices not fixed on any device shipped by the manufacturer. This is related to the Median Active Vulnerabilities (MAV) measure~\cite{Wright2014} but is the mean rather than the median, as this gives a continuous value.
  An example is given in Figure~\ref{fig:mcalculation}.
%TODO should we compute the median instead?
\end{description}

@@

$f$ is hard to game without doing a good job at security but it doesn't get any worse if there is already one known vulnerability and another is found.
A high value of $u$ could be achieved by only ever shipping one version but that would give low values for $f$ and $m$ (and not be attractive to new customers).
A high value of $m$ could be achieved by focusing on only one device at a time and ensuring that gets updates but ignoring all others, but that would lower $f$ and $u$.

@@

The scores across the whole of android are that \daMeanInsecurityPerc\ of devices are exposed to known root exploits.
There are on average \daMeanOutstandingVulnerabilities\ outstanding vulnerabilities not fixed on any device.
Only on average \daUpdatednessPerc\ of devices run the most recent version of Android.
This gives a security score of \daSecurityScore / 10.
\daTabSecScoressummary
However there are a wide variety of scores depending on the source of the device.
There have been many reports that Google's Nexus devices are better at getting updates than other Android devices because Google makes the original updates and ships them to its devices.
Table~\ref{tab:sec_summary} shows that this is the case with Nexus devices getting much better scores than non-Nexus devices.
\daTabSecScoresmanufacturer
Different manufacturers have very different scores, Table~\ref{tab:sec_manufacturer} shows the scores for the \daNumSigManufacturers\ manufacturers with a significant presence in our data with \daSecScoreBestmanufacturer\ (\daSecScoreBestmanufacturerScore\ / 10) doing best and \daSecScoreWorstmanufacturer\ (\daSecScoreWorstmanufacturerScore\ / 10) doing worst.
Manufacturers are considered significant if we have data from at least \daSigNumDevices\ devices and at least \daSigNumDeviceDays\ days of contributions.
\daTabSecScoresmodel
Even within manufacturers different models can have very different update behaviours and hence security.
Table~\ref{tab:sec_model} shows the results for the \daNumSigModels\ device models which have a significant presence by the same metric with \daSecScoreBestmodel\ (\daSecScoreBestmodelScore\ / 10) doing best and \daSecScoreWorstmodel\ (\daSecScoreWorstmodelScore\ / 10) doing worst.

>>>>

This score is computed from several components:
\begin{description}
  \item[$f$] The proportion of the time where devices were free from known critical vulnerabilities. This is equivalent to Acer and Jackson's proposal~\cite{Acer2010} to measure the security based on the proportion of users with at least one unpatched critical vulnerability and similar to the Vulnerability Free Days (VFD) score~\cite{Wright2014}.
  Unlike VFD this is the proportion of running devices which were free from critical vulnerabilities, rather than days which the manufacturer was free from outstanding critical vulnerabilities as that does not take account of the update process.
  \item[$u$] The proportion of devices which run the latest version of Android shipped to any device produced by that manufacturer. This is a measure of internal updatedness, a low score would mean many devices are being left behind.
  This assumes that newer versions are better with stronger security, historically steps have been taken to improve Android security in newer versions so this assumption should generally hold, but sometimes new updates introduce new vulnerabilities.
  \item[$m$] The mean number of outstanding vulnerabilities affecting devices not fixed on any device shipped by the manufacturer. This is related to the Median Active Vulnerabilities (MAV) measure~\cite{Wright2014} but is the mean rather than the median, as this gives a continuous value.
  An example is given in Figure~\ref{fig:mcalculation}.
%TODO should we compute the median instead?
\end{description}

@@

$f$ is hard to game without doing a good job at security but it doesn't get any worse if there is already one known vulnerability and another is found.
A high value of $u$ could be achieved by only ever shipping one version but that would give low values for $f$ and $m$ (and not be attractive to new customers).
A high value of $m$ could be achieved by focusing on only one device at a time and ensuring that gets updates but ignoring all others, but that would lower $f$ and $u$.
One way to influence our scores would be to add additional devices to Device Analyzer which have good security, these would have to be real end user devices as we could detect fake ones, this would increase the size of our data set and would require providing genuinely good security to some users.

@@

The scores across the whole of android are that \daMeanInsecurityPerc\ of devices are exposed to known root exploits.
There are on average \daMeanOutstandingVulnerabilities\ outstanding vulnerabilities not fixed on any device.
Only on average \daUpdatednessPerc\ of devices run the most recent version of Android.
This gives a security score of \daSecurityScore / 10.
\daTabSecScoressummary
However there are a wide variety of scores depending on the source of the device.
There have been many reports that Google's Nexus devices are better at getting updates than other Android devices because Google makes the original updates and ships them to its devices.
Table~\ref{tab:sec_summary} shows that this is the case with Nexus devices getting much better scores than non-Nexus devices.
\daTabSecScoresmanufacturer
Different manufacturers have very different scores, Table~\ref{tab:sec_manufacturer} shows the scores for the \daNumSigManufacturers\ manufacturers with a significant presence in our data with \daSecScoreBestmanufacturer\ (\daSecScoreBestmanufacturerScore\ / 10) doing best and \daSecScoreWorstmanufacturer\ (\daSecScoreWorstmanufacturerScore\ / 10) doing worst.
Manufacturers are considered significant if we have data from at least \daSigNumDevices\ devices and at least \daSigNumDeviceDays\ days of contributions.
Additionally for $m$ and $u$ we ignore days with less than \daSigNumDevicesDay\ devices contributing to that day's score.
\daTabSecScoresmodel
Even within manufacturers different models can have very different update behaviours and hence security.
Table~\ref{tab:sec_model} shows the results for the \daNumSigModels\ device models which have a significant presence by the same metric with \daSecScoreBestmodel\ (\daSecScoreBestmodelScore\ / 10) doing best and \daSecScoreWorstmodel\ (\daSecScoreWorstmodelScore\ / 10) doing worst.
